\documentstyle[12pt,preprint,times]{aastex}
\begin{document}

\pagestyle{empty}
%\pagenumbering{arabic}


\noindent
\hskip -0.8cm {\bf Dennis Zaritsky}

\vskip -8pt
\noindent
Steward Observatory, University of Arizona, Tucson, AZ, USA

\smallskip
\noindent
\underbar{\bf Program Role: }
Study of low surface brightness galaxies vs. environment. Optical/IR observing expertise.

\smallskip
\noindent
\underbar{\bf Current Positions:}



\vskip -5pt
\noindent
2002$-$Present: Professor/Astronomer, Steward Observatory, Univ. of Arizona

\vskip -8pt
\noindent
2012$-$Present: Deputy Director, Steward Observatory, Univ. of Arizona


\vskip -8pt
\noindent
2014$-$Present: Associate Editor, Science Advances


\smallskip
\noindent
\underbar{\bf Former Positions:}

\vskip -5pt
\noindent
1999$-$2002: Associate Professor/Associate Astronomer, Steward Observatory, Univ. of Arizona

\vskip -8pt
\noindent
1997$-$2000 : Associate Professor/Associate Astronomer, Lick Observatory, 
UC Santa Cruz

\vskip -8pt
\noindent
1994$-$1997 : Assistant Professor/Assistant Astronomer, Lick Observatory, 
UC Santa Cruz

\vskip -8pt
\noindent
1991$-$1994 : Hubble Fellow at the Carnegie Observatories



\smallskip
\noindent
\underbar{\bf Education:}
California Institute of Technology, Pasadena, CA; B.S. in Physics  with Honor, 1986;
University of Arizona, Tucson, AZ; Ph.D. in Astronomy, 1991



\smallskips
\noindent
\underbar{\bf National and International Committees:}
NOAO DataLab Design Review Committee (2016), NASA Astrophysics Senior Review (2016), DESI Technical Document Red Team Reviewer (2015), NSF/NOAO PRP committee (2015), NSF Gemini Review (2015), Columbia University External Review Committee (2015), Hubble Fellowship Selection Panel (2015), ESO Spectroscopic Survey Review Panel (2013-2015)

\smallskip
\noindent
\underbar{\bf Honors:}
Hubble Fellowship (1991), E.F. Fullam Award (1993), David and Lucile Packard Fellowship (1997), Sloan Fellowship (1998), NSF CAREER award (1998), Newton Lacy Pierce Prize (1999), Guggenheim Fellowship (2006), Galileo Circle Fellowship (2017)

\noindent
\underbar{\bf Publications:} Currently 216 refereed publications, a total of 17909 citation, and an H-index of 71 (Google Scholar). Examples include:

\vskip -5pt
\noindent
The Massive Halos of Spiral Galaxies 1994. Zaritsky, D. and White, S.D.M, ApJ, 435, 599\hfil 

\vskip -8pt
\noindent
H II Regions and the Abundance Properties of Spiral Galaxies
1994 Zaritsky et al.,  Ap. J, 420, 87

\vskip -8pt
\noindent
A Direct Empirical Proof of the Existence of Dark Matter 2006. Clowe, D., Bradac, M., Gonzalez,\hfil

\vskip -8pt
\hskip 1cm A.H., Markevitch, M., Randall, S., Jones, C., and Zaritsky, D. Ap. J. Letters 648, 108

\vskip -8pt
\noindent
A Census of Baryons in Galaxy Clusters and Group, 2007, Gonzalez et al., ApJ, 666, 147

\vskip -8pt
\noindent
The Star Formation History of the Large Magellanic Cloud 2009. Harris, J. and Zaritsky, D., AJ,\hfil

\vskip -8pt
\hskip 1cm
138, 1243

\end{document}
